Bioverse: Origins of Life

### 2024-07-19 src/tex/ms.tex
upload current draft
move figure to results

\begin{abstract}
    tbd.
\end{abstract}

\section{Introduction}
\label{sec:intro}
\todo[inline]{Introduce OOL, the importance of planetary contexts}

\subsection{Origins of Life Scenarios and their Predictions}\label{sec:predictions}
\todo[inline]{Present widely discussed OOL scenarios and their predictions on exoplanet observables; derive testable hypotheses.}
\label{sec:ool_scenarios}
In this section, we present some of the most prominent origins of life scenarios and their observational predictions.
We focus on the necessary environmental conditions for the processes and reactions inherent to each scenario, and aim to identify distinct observables that are accessible via present and near-future remote sensing techniques.

@@

\begin{figure}
    \script{inhabited_FGKM.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/inhabited_FGKM}
        \caption{Host stars of all transiting \glspl{EEC} and inhabited planets in a simulated transit survey.
        In the FGK sample, most \glspl{EEC} and all inhabited planets orbit K~dwarfs.
        In an M~dwarf sample of the same size, the fraction of inhabited planets is larger.
        }
        \label{fig:inhabited_FGKM}
    \end{centering}
\end{figure}

As shown in Figure~\ref{fig:inhabited_FGKM}, the majority of \glspl{EEC} orbit lower-mass stars.
The fraction of inhabited planets is highest in the M~dwarf sample due to the higher \gls{NUV} fluxes in the \gls{HZ} of these stars.

@@

\subsection{Survey simulations with Bioverse}\label{sec:results-bioverse}

In a magnitude- and volume-limited sample of a transit survey, the host star distribution will be skewed toward later spectral types and dominated by M~dwarfs (see Figure~\ref{fig:inhabited_FGKM}).
Due to how the \gls{HZ} scales with spectral type, by far most transiting \glspl{EEC} occur around M~dwarfs.
Their \gls{NUV} fluxes are generally highest at early times $\lesssim\SI{100}{\mega\year}$.
These host stars, in particular late subtypes, also provide extended periods of increased \gls{NUV} emission that overlap with times when some of these planets occupy the \gls{HZ} (see Figure~\ref{fig:hz_nuv_evo}), our requirement for abiogenesis (compare Equation~\ref{eq:hypothesis-uv}).
Because of that, all inhabited planets in our magnitude- and volume-limited sample orbit M~dwarfs.

>>>>

\begin{abstract}
    ...
\end{abstract}

\section{Introduction}
\label{sec:intro}
\todo[inline]{Introduce OOL, the importance of planetary contexts}
...
\subsection{Origins of Life Scenarios and their Predictions}\label{sec:predictions}
\todo[inline]{Present widely discussed OOL scenarios and their predictions on exoplanet observables; derive testable hypotheses.}
\label{sec:ool_scenarios}
In this section, we present some of the most prominent origins of life scenarios and their observational predictions.
We focus on the necessary environmental conditions for the processes and reactions inherent to each scenario, and aim to identify distinct observables that are accessible via present and near-future remote sensing techniques.

@@

@@

\subsection{Survey simulations with Bioverse}\label{sec:results-bioverse}
\begin{figure}
    \script{inhabited_FGKM.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/inhabited_FGKM}
        \caption{Host stars of all transiting \glspl{EEC} and inhabited planets in a simulated transit survey.
        In the FGK sample, most \glspl{EEC} and all inhabited planets orbit K~dwarfs.
        In an M~dwarf sample of the same size, the fraction of inhabited planets is larger.
        }
        \label{fig:inhabited_FGKM}
    \end{centering}
\end{figure}
In a magnitude- and volume-limited sample of a transit survey, the host star distribution for \glspl{EEC} will be skewed toward later spectral types and dominated by M~dwarfs due to how the \gls{HZ} scales with spectral type.
For a fixed planet sample size, the fraction of inhabited planets is highest in the M~dwarf sample due to the higher \gls{NUV} fluxes in the \gls{HZ} of these stars (see Figure~\ref{fig:inhabited_FGKM}).
Their \gls{NUV} fluxes are generally highest at early times $\lesssim\SI{100}{\mega\year}$.
These host stars, in particular late subtypes, also provide extended periods of increased \gls{NUV} emission that overlap with times when some of these planets occupy the \gls{HZ} (see Figure~\ref{fig:hz_nuv_evo}), our requirement for abiogenesis (compare Equation~\ref{eq:hypothesis-uv}).
Because of that, all inhabited planets in our magnitude- and volume-limited sample orbit M~dwarfs.
